\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-02 manuscript.Rmd
Table abnd figs

```{r MAPefa, include=FALSE}
#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
```

@@

devtools::install_github("unDocUMeantIt/koRpus")
library(koRpus)# stable release
koRpus::install.koRpus.lang(lang=c("en"))
library(koRpus)
library(koRpus.lang.en)

@@

48 items were generated by an expert panel and  administered to a large sample (n = `r nrows(EFA.descriptives)` to explore the latent structure. Exploratory factor analysis revalied a five factor solution with 25 items. ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime"). These five factors dealt with different light exposure related behavior. The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`. As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.

A CFA on a separate sample ((n = `r nrows(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item. The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, Mcdonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.

Lastly, we developed a short-LEBA (n=23) using IRT analysis. We fitted a graded response model model to the combined efa and cfa sample ( n =`r nrows(data)`). We discarded 5 items with relatively flat item information curve [I($\theta$) <.20]. No item was identified as a misfit item.  In terms of item difficulty, our scale contained very high  high , moderate , and low discriminating items and covered a substantial range of underlying  attributes.  Test information curve also indicated a good coverage of underlying trait continuum with precision. 
## Conclusion
"The Light exposure behavior assessment"(LEBA) gave a five solution with 25 items in an exploratory factor analysis. A confirmatory factor analysis with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 25-item "Bangla version of Rotter’s I-E scale"LEBA" was found reliable and valid. A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18 item scale with  a good range of covergange across the underlying trait continuum. All-in-all, we can recommend both forms to be used to capture individual’s light exposure related behavior

>>>>

```{r MAPefa, include=FALSE}
#MAP
map <- psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
map.map <- as.data.frame(map$map)
colnames(map.map) <- "MAP Statistic"
map.statistics <- map$vss.stats[,c(1,2,5,6,7,10,11)]
full.map <- cbind(map.map,map.statistics)

write.csv(full.map, "Table_raw/map_stat")
```

@@

#devtools::install_github("unDocUMeantIt/koRpus")
library(koRpus)# stable release
#koRpus::install.koRpus.lang(lang=c("en"))
library(koRpus)
library(koRpus.lang.en)

@@

48 items were generated by an expert panel and  administered to a large sample (n = `r nrow(EFA.descriptives)` to explore the latent structure. Exploratory factor analysis revalued a five factor solution with 25 items. ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime"). These five factors dealt with different light exposure related behavior. The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`. As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.

A CFA on a separate sample ((n = `r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item. The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, Mcdonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.

Lastly, we developed a short-LEBA (n=23) using IRT analysis. We fitted a graded response model model to the combined efa and cfa sample ( n =`r nrow(data)`). We discarded 5 items with relatively flat item information curve [I($\theta$) <.20]. No item was identified as a misfit item.  In terms of item difficulty, our scale contained very high  high , moderate , and low discriminating items and covered a substantial range of underlying  attributes.  Test information curve also indicated a good coverage of underlying trait continuum with precision. 
## Conclusion
"The Light exposure behavior assessment"(LEBA) gave a five solution with 25 items in an exploratory factor analysis. A confirmatory factor analysis with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 25-item "Bangla version of Rotter’s I-E scale"LEBA" was found reliable and valid. A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18 item scale with  a good range of covergange across the underlying trait continuum. All-in-all, we can recommend both forms to be used to capture individual’s light exposure related behavior
